Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-08-23 research_class/paper.tex
paper.tex: add chat images.

@@

\title{Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)} % title

\author{Joel D. Martin and David Levine
\thanks{University of Texas at Arglington}
}

@@

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
chat application using WebRTC, PeerJS and Raft.js. WebRTC is
a protocol that modern browsers have begun to integrate which enables
browser-to-browser communication. PeerJS is a WebRTC client library
and extensible signalling server. Raft.js is an implementation in
JavaScript of the Raft distributed consensus protocol. These
technologies are combined to create a chat application that guarantees
a shared, consistent and linearized view of the chat history without
relying on a single centralized server. We also create a series of
automated tests using the SlimerJS browser automation tool and use
them to show the correctness of the chat application and also to
measure the performance and scalability of the application over
various cluster sizes.
\end{abstract}

@@

\begin{figure*}[h]
\centerline{\includegraphics[width=0.8\textwidth]{raft_rtc_architecture}}
\caption{Raft over RTC Architecture}
  \label{fig:raft_rtc_architecture}
\end{figure*}

@@

\begin{figure*}[h]
\centerline{\includegraphics[width=0.8\textwidth]{raft_rtc_sequence}}
\caption{Raft over RTC Sequence Diagram}
  \label{fig:raft_rtc_sequence}
\end{figure*}

@@

\begin{center}
    \includegraphics[width=0.4\textwidth]{browser_1.png}
    \captionof{figure}{Raft over WebRTC Browser with One Node}
    \label{fig:browser_1}
\end{center}

@@

%\begin{figure*}[Ht]
%\centerline{\includegraphics[width=15cm]{browser_2}}
%\caption{Raft over WebRTC Browser with Five Node}
%  \label{fig:browser_2}
%\end{figure*}

\begin{center}
    \includegraphics[width=0.4\textwidth]{browser_2.png}
    \captionof{figure}{Raft over WebRTC Browser with Five Nodes}
    \label{fig:browser_2}
\end{center}

@@

>>>>

\usepackage{authblk}

\usepackage{microtype}

@@

\title{Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)}

\author{Joel D. Martin}
\author{David Levine}
\affil{University of Texas at Arglington}

@@

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
application using WebRTC, PeerJS and Raft.js. WebRTC is a protocol that modern
browsers have begun to integrate which enables browser-to-browser
communication. PeerJS is a WebRTC client library and extensible signalling
server. Raft.js is an implementation in JavaScript of the Raft distributed
consensus protocol. These technologies are combined to create a chat
application that guarantees a shared, consistent and linearized view of the
chat history without relying on a single centralized server. We also create a
series of automated tests using the SlimerJS browser automation tool and use
them to show the correctness of the chat application and also to measure the
performance and scalability of the application over various cluster sizes.
\end{abstract}

@@

\begin{figure*}[h]
\centerline{\includegraphics[width=0.8\textwidth]{imgs/raft_rtc_architecture}}
\caption{Raft over RTC Architecture}
  \label{fig:raft_rtc_architecture}
\end{figure*}

@@

\begin{figure*}[h]
\centerline{\includegraphics[width=0.8\textwidth]{imgs/raft_rtc_sequence}}
\caption{Raft over RTC Sequence Diagram}
  \label{fig:raft_rtc_sequence}
\end{figure*}

@@

\begin{center}
    \includegraphics[width=0.45\textwidth]{imgs/browser_1.png}
    \captionof{figure}{Basic app with one Node/Tab}
    \label{fig:browser_1}
\end{center}

@@

\begin{center}
    \includegraphics[width=0.45\textwidth]{imgs/browser_5.png}
    \captionof{figure}{Basic app with Five Nodes/Tabs}
    \label{fig:browser_5}
\end{center}

@@

\begin{center}
    \includegraphics[width=0.45\textwidth]{imgs/chat_1a.png}
    \captionof{figure}{Chat app with one Node/Tab}
    \label{fig:browser_chat_1}
\end{center}

\begin{center}
    \includegraphics[width=0.45\textwidth]{imgs/chat_5a.png}
    \captionof{figure}{Chat app with Five Nodes/Tabs}
    \label{fig:browser_chat_5}
\end{center}
